A game of competition over risk

### 2023-04-20 paper/article.tex

>>>>

\begin{result}

    Penalties $C$ decrease the average risk taken $\bar r$. Market frictions $\tau$ decrease the average risk taken and increase the total reward $u$. Market frictions have more impact on the total reward in high-penalty environments.
    In particularly inefficient markets with high $\tau$, increasing penalties can counterintuitively improve cooperation and the total reward.
\end{result}

We illustrate that behavior in Figure \ref{fig:result-noise}.

\begin{figure}[htbp]
  \centering
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{equilibria_rbar_u_tau}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{equilibria_rbar_u_C}
  \end{minipage}
  \caption{The two figures represent the same points with different level lines: constant $C$ and constant $\tau$. At constant $C$ we observe a linear relationship between $u$ and $\bar r$ when changing $\tau$. We also observed that behavior for all values of $\rho$.}
  \label{fig:result-noise}  
\end{figure}

\begin{result}
    Players take more risks in environments of negative correlation. Negative correlation improves their payoff compared to an absence of correlation.

    Players take less risks in environments of positive correlation. The impact on performance is negative in efficient markets but can become positive in noisy markets.
\end{result}

We illustrate that behavior in Figure \ref{fig:result-corr}.

\begin{figure}[htbp]
  \centering
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{equilibria_rbar_corr_C=0}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{equilibria_rbar_corr_C=1}
  \end{minipage}
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{equilibria_u_corr_C=0}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
    \centering
    \includesvg[width=1.1\linewidth]{equilibria_u_corr_C=1}
  \end{minipage}
  \caption{}
  \label{fig:result-corr}  
\end{figure}
